### 2020-06-19 Documents/ESA/sections/LitReview.tex
Updated ESA

\begin{enumerate}
    \item Scalable
    \item Distributed
    \item Generality
    \item Low Computational Load
    \item Robustness
\end{enumerate}

We will use these metrics, alongside the problem statement to approach the current literature
surrounding the theory and practices of Multi-Agent Systems.

@@

\textbf{Add in more recent literature r.e. learning in stochastic games}

@@

>>>>

\begin{enumerate}
    \item Distributed. It will often be the case that a multi-agent system must spread out across a
    large area or operate in regions where communication is limited. As such it is beneficial that
    such a system does not rely too heavily on communication with a central body. The individual
    agents must, therefore, be able to make their own decisions and act as independent entities.
    Aside from the advantage of communication, this ensures that the system is not tied to a single
    point of failure; in a system governed by a centralised decision maker, any faults in the
    central body propagates throughout the group. Of course, this comes at the price of
    computational load - if the agents are required to act independently, they must possess the
    resources to do so. The term distributed should not be confused with decentralised. The latter
    refers to a regime in which agents all communicate with one another before making a decision.
    Whilst this is preferable to a centralised decision maker in terms of the requirement for one
    entity to communicate with all agents, it still places a high cost on the requirement that
    agents be in constant communication with one another. In fact it may pose the additional risk
    that if any agent in the team fails, the whole pipeline falls apart. Distributivity, on the
    other hand, requires that agents make independent decisions so that, though agents may
    communicate with each other, they are still able to operate when this is not possible.
    \item Generality. MAS come in many different flavours; sometimes a small group of heterogeneous 
    (agents with different capabilities) agents may be required to perform a delicate task whilst
    in others, it may be required that a large population of homogeneous (all of the same type)
    agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
    strategy whilst in the middle of a task. It would be a hindrance if the agents were required to
    be reprogrammed with a completely different control methodology each time the situation changes
    slightly. It would be preferable if the method could apply to all different types of scenarios,
    with homogenous or heteregeneous agents, with single tasks or multiple, in any environment with
    only minor customisation required. Better still if the agents are able to adapt themselves to
    the specifics of the scenario.
    \item Low Computational Load. As mentioned in the previous chapter, a MAS will often be used in
    complex situations, many of which will be too dangerous for human intervention. As such, the
    system will be required to carry out its tasks online. For this reason, it is vital that the
    control method be one which produces low computational load - especially where the time frame
    for adjusting agent behaviour is limited. Monetary concerns also play a part in this metric; it
    would not do to impose that every member of the team be equipped with high performance computing
    power as this would likely fall outside of the budget of any practical usage.
    \item Robustness. Particularly for physical robots, a MAS should be able to operate in
    situations which present sensor noise, communication noise, latency, and environmental
    disturbances. This is rather important in unseen environments where full a priori knowledge of
    the map cannot be assumed.
    \item Scalable. This is mentioned last since the ability for a MAS to scale comes from its
    distributivity  and low computational load. Scalability is the capacity for any method of
    controlling a MAS to successfully operate as the size of the team increases. This, of course, is
    related to the complexity of the algorithms involved. However, it should be noted that it is not
    always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the
    task at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to
    perform the task, rather than a large population. 
\end{enumerate}

We begin by presenting a subset of the vast array of literature regarding MAS and focus on those
which are relevant to the study at hand. We conclude this chapter by providing some remarks about
how these methods hold against the above metrics.

@@

\textbf{Add in more recent literature r.e. learning in stochastic games and the robustness of MARL}

@@

Each of the above methods present different advantages in their approach towards MAS, as well as a
particular set of disadvantages.

Game Theoretic methods have long provided a rigorous approach for
modelling the behaviour of any MAS. It places no limitation on the heterogeneity of the agents or
the task demanded. An appropriate choice of payoff matrices will account for both of these
specifications. Recent advances in POSGs have lifted the strong assumptions on prior knowledge that
was required to achieve a Nash Equilibrium and Game Theoretic Control allows for such methods to be
applied in continuous state spaces. Whilst the latter shows particular promise, game theoretic
methods still fall short in terms of distributivity as they are heavily reliant on communication
with a centralised decision maker to supply rewards, or within the team to determine each others'
actions. They also require a priori knowledge of the situation in order to set up payoff matrices
and so cannot be regarded as robust to environmental uncertainty.

Multi-Agent Reinforcement Learning builds on the latter two shortcomings of game theory by allowing
the environment to supply rewards to agents who adapt their behaviour accordingly. MARL is proving
to be a powerful method to control MAS, and is rapidly improving, but cannot yet be regarded as
robust. Studies repeatedly show that small alterations or noise in the environment can result in
large deviations in behaviour. Furthermore, few guarantees can be placed on the resulting behaviour
of a MARL system, though progress is being made in closing this gap.

Control Theory, on the other hand, takes pride in the guarantees placed on the MAS such as:
controllability, stability, and robustness. However, control techniques are often centralised or
decentralised. Distributed methods of control is still an evolving field, particularly in terms of
robustness to uncertainty. In order to establish guarantees, assumptions are also made on the
specifics of the MAS, and so control theoretic methods have yet to evolve into general,
heterogeneous systems with any given task.

Swarm systems have their strongest advantage in scalability and, in fact, swarm techniques are built
to scale due to the distributivity and low computational load placed on each agent. This has often
come with the assumption that agents in the swarm act as simple, homogeneous, particles who follow
very simple rules of interaction. Recent work is showing that this is not a necessary assumption
and, in fact, swarms can leverage heterogeneity and agent capabilities to ensure robustness and
generalisation.

It is clear that each method presents its own set of advantages and disadvantages. In fact, the
greater contributions are made from a unification of techniques (e.g. game theoretic control) which
leverage the strengths of one technique to mitigate the drawbacks of another. To this end, we
consider the unification of swarm control and multi-agent learning. The aim is to unify the
strengths of swarm theory, MPC and game theory to study populations of agents who can make
decisions on an individual basis but perform tasks through large scale collaboration. In the
subsequent chapters, we propose a line of research which explores the properties of a system as well
as establishing practical control methodologies along the way.

### 2020-06-19 Documents/ESA/sections/ProposedResearch.tex
Updated Write Up and ESA
Updated ESA

\begin{document}
    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
\end{document}

>>>>

\begin{document}

	This chapter describes a proposed line of research which aims to study the evolution of swarm
	systems with independent, learning agents under the influence of predictive controls. We detail
	the novel lines of research which this work aims to undertake, providing suggestions of the
	hypotheses posed by these lines. With this in mind the following studies are proposed and
	developed subsequently:

	\begin{itemize}
		\item \textbf{Stability and Chaos in MARL:} in which we seek to understand the dynamics of
		agent strategies when using Q-Learning to learn a game through iteration. We will establish
		the stability, as a function of parameters, when learning general p-player N-action games.
		This study enables the appropriate selection of parameters and payoff matrices to ensure the
		stability of the strategies of a finite set of agents, such as leaders in a swarm.
		\item \textbf{Dynamics of Mean-Field Q-Learning Games:} in which we examine the
		strategy dynamics for large populations of agents learning through iterated games and
		mean-field Q-Learning. We seek to understand the long term behaviour of such mean-field
		systems in terms of its strategy selection. This study extends the previous and allows for
		the stability of the strategies of a population of agents to be established.
		\item \textbf{Model Predictive Control of Active Particles through Fields:} in which we
		investigate the interaction of a swarm of active particles with potential fields. We
		establish the stabilisability of an MPC scheme with defined stage costs, as well as an
		analysis of the suboptimality of the method.
		\item \textbf{Incorporation of Intelligence in Control:} in which we adapt the dynamical
		system from the above point to include an interaction term, accounting for strategy
		selection by agents who learn through iterated games against one another. Interactions with
		an MPC scheme is then to be examined in a similar capacity.

	\end{itemize}

	\textbf{TODO: Ensure all references here are in the Lit Review}

    \section{Stability and Chaos in MARL} \label{sec::Chaos_in_MARL}

    This segment of research is aimed towards a deeper understanding of the strategy evolution
    of agents following a Q-Learning approach. This allows for guarantees to be placed on the
    behaviour of such agents, in particular the conditions under which the game will converge to a
    stable equilibrium.

    It has long been established that, upon lifting the strong assumptions made by traditional
    game theory (such as the rationality of agents and complete information), that player
    strategies can result in much more complex behaviour than convergence to a Nash Equilibrium 
    (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
    as tic-tac-toe and prisoner's dilemma \cite{Galla's work and I think Sato's work}. These
    behaviours include: convergence to a unique equilibrium (though not always to an NE),
    convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
    Figure ... Of these, the most preferable is, of course, convergence to a unique equilibrium,
    although it is still possible to study systems with multiple equilibria or limit cycles 
    \cite{One of the textbooks}. However, it would be difficult to control systems whose dynamics
    are governed by chaos (though research into controlling chaos is ongoing and rife with
    opportunity \cite{CyberneticalPhysics}) and so MARL techniques should avoid this. It would,
    therefore, be a useful endeavour to determine the conditions under which these sorts of
    behaviours arise.

    The behaviour of a system may be studied given a model of its dynamics. It is through this
    process that a wide array of physical systems, from harmonic pendulums to geophysical fluids,
    can be understood. A growing body of research aims to understand multi-agent reinforcement
    learning through the lens of its dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames}
    were able to derive a model of the strategy evolution of agents learning through iterated games.
    Through this, they were able to arrive at the following model of Multi-Agent Q-Learning

	\begin{subequations}
	\label{eqn::EOM}
		\begin{equation}
			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
		\end{equation}
	\end{subequations}

	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
	predict the expected behaviour of Q-Learning agents, as shown in Figure ...

	It is clear, both from (\ref{eqn::EOM}) and Figure ... that the long-term strategy selection of
	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
	then pose the question: how do these elements influence the types of behaviours seen during
	learning on an iterated game? In other words, under what parameter selections are we likely to
	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?

	With this in mind, the intention of this area of study is to consider the analysis presented in
	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
	learning behaviour of human players in a game \cite{whatevertheycite}. The authors are able to
	determine the regions of parameter space in which complex behaviour,
	including cycles and chaos, predominantly occur and those in which a given game converges to a
	stable equilibrium. Figure ... reproduces the graphs shown in \cite{Sanders2018} which
	illustrates the successful derivation of a 'phase line', across which learning shifts from
	convergent to chaotic.

    We propose to bridge the analysis presented by Sanders
    et al. and Galla et al. towards games learnt using MARL, particularly Q-Learning with
    Boltzmann exploration as considered by Tuyls et al. This would allow for a characterisation of
    the expected resultant behaviour under given parameters for a particular game. The vision for
    this is to provide guarantees on the stability of a finite set of agents within a swarm, such as
    leaders in a flock. Without this, it would be impossible to ensure the stability of a swarm in
    which intelligent, social interactions must be accounted for. However, this analysis
    would also allow for a characterisation of the conditions under which MARL algorithms may
    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
    payoff matrices and parameters accordingly.

    This segment of research is currently underway and approaching completion. The analysis can be
    seen in Section \ref{sec::Chaos_in_Q-Learning}.

    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}

    This segment of research aims to model the game dynamics of large populations of agents
    learning through iterated games and mean-field Q-Learning. The aim is to provide similar
    guarantees of stability as in the previous sections with the caveat that all agents in the
    population can learn, rather than a finite subset.

    One of the main results shown by Sanders et al. \cite{Sanders2018} is that as the number of
    players in a game increases, the learning behaviour is more likely to be chaotic, regardless of
    the choice of parameters. This is intuitive since a higher number of players would result in a
    greater strategy space and more agents for any particular player to learn against and is
    verified by their presented results as in Figure ...

    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
    cursory verification of this intuition. Here, the authors present an anaysis of the learning
    dynamics for a large agent population (which they approximate as containing infinite agents)
    where each agent is an independent Q-Learning using Boltzmann action selection. The
    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
    strong predictor of the overall strategy selection of the population. Indeed, rather than
    examining the strategies of every agent in the population (which the authors approximate as
    infinitely large), they model the evolution of a probability density function which, for each
    action, defines the density of agents who retain a given Q-value for that action. This is
    illustrated in Figure ...

   	As the authors point out, this is the first attempt at considering such a problem, and relies on
	heavy assumptions. The strongest of these is placed on the game itself, which is always
	assumed to be cooperative (in Sanders' terms, $\Gamma = 1$). We, therefore, propose extending
	this model to accomodate an arbitrary choice of games.

	Two proposals for how this might work

	\begin{itemize}
		\item Estimate the population state using a Random Finite Set (RFS) and apply the models
		from the previous study. This is a new hypothesis so more research is required.
		\item Decompose a generic game into a weighted sum of a competitive and a cooperative game.
		Treat these as two separate agents and invoke the mean field approximation so that any given
		agent is effectively engaged in a three-player game where the strategy of the opponents is
		the average strategy of the population.
	\end{itemize}

	\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}

    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}

    Here we aim to study the interaction of a swarm of 'active particles' with a potential field. In
    particular this field is to be generated by 'field particles'. A model predictive control 
    (MPC) scheme
    is to be devised to drive this system to desired configurations, with guarantees placed on
    stability and satisfaction of input constraints. The sub-optimality of the control
    scheme is to be studied.

    As described in the previous chapter, the control of swarms has been examined through the use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Zhang2018, Elamvazhuthi2019, Li2017,
    BorziCollectiveMotion}, though it makes the assumption that the system evolves through 'drifted
    brownian motion'. This means that the agents are considered to move about independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Any paper of Fokker Planck control}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{VlasovMPC}.

	The hypothesis of this section is that the distribution of active particles, whose evolution is
	described through a Vlasov equation, may be controlled through the influence of a scalar field
	generated by 'field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
	\cite{Bellomo2017}

	\begin{equation}
	\label{eqn::Vlasov}
    \begin{split}    
        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
        = \epsilon Q(f, f) \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*, 
    \end{split}
    \end{equation}

    Here, $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$ which represents the state of
    the system. $\kappa \geq 0$ is a scalar
    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
    {v}^*$) gives the position in phase space of a 'field particle'. It can be seen that the these
    field particles influence the velocity of the swarm agents.

	The contribution that this study presents over those using brownian motion is the inclusion of an
	interaction operator $Q(f, f)$. This governs how agents interact with one another. With this
	term included, the dynamics account for the tendency of agents to avoid collisions. However,
	the term is intended to account also for social interactions between agents, which we aim to
	leverage in the subsequent section.

	The complexity of this interaction term will need to be gradually increased over time. To begin
	with, we may entirely neglect this term. It is here that we will compare the model proposed by Zhang
	with that proposed by Bellomo et al. We may then consider only local interactions, which is typical
	for most swarming systems in the current literature, before then considering non-local interactions.
	This provides the scope for swarms to interact with a greater number of agents. At this stage, we
	may expand our study to consider the presence of interaction domains. This places constraints on how
	agents may interact with one another, allowing for a greater generalisation of inter-agent
	interactions. Ultimately, we would like to influence the interaction term, though this is discussed
	in Section \ref{sec::Intelligence_in_control}. The questions we will
	consider here are:

	\begin{itemize}
		\item The stablity of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner?
		\item The guarantees of the system: Is it possible to ensure that controls remain within an
		admissible set (typically a closed, bounded and convex set \cite{PDEControl}).
	\end{itemize}

	These results will be established theoretically alongside the sub-optimality of the MPC scheme
	and verified through numerical simulations in a 2D environment. It
    will be of interest to perform a similar analysis to Ko and Zuazua \cite{Ko2019} in which the
    cost functional is altered to favour particular metrics  (e.g. running cost, control time etc.)
    and also analyse the effect of varying the time horizon.

    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}

    This section of the study is perhaps the strongest extension proposed in this
	chapter, and will likely be the most challenging. Here, we examine the dynamics (
	\ref{eqn::Vlasov}) in which the interaction term accounts for the social dynamics of the
	decision making of individual agents who have learnt through an iterated game. We leverage the
	strategy evolution dynamics and stability analysis established in 
	\ref{sec::Chaos_in_MARL} and \ref{sec::Large_Agent_Dynamics}.

	Two proposals for incorporation of social interaction:
	\begin{itemize}
		\item Addition of the agent decisions as a constant in the state $f$. This should be fine if
		it's fixed but note that the controls have no influence over this.
		\item Multiplicative term in the turning probability which acts as a weighting term where
		weights are equal to the agent strategy. This extends to both the swarms in
		which the leaders are making decisions (only leaders have this term) as well as in
		swarms where the population makes decisions (everyone has this term). This will need to be
		done with care though to ensure that normalisation holds.
	\end{itemize}

	The MPC scheme from the previous section will then be adapted to this dynamical system with the
	same questions of well-posedness and stability considered.

	A possible extension of this would be to consider online learning by incorporating the time
	evolution of the strategy space within the social interaction term, which would now be
	time-varying. The proper integration of these dynamical systems would depend on the form of the
	systems derived in Section \ref{sec::Large_Agent_Dynamics} and it is likely that relaxations would
	be required in terms of controllability results. A likely relaxation would be to examine only the
	behaviour in the long-enough time frame, which means that we could not impose a final time. Of
	course, this means that we could only consider optimal control rather than model predictive.
	However, without establishing the models from Section \ref{sec::Large_Agent_Dynamics}, this
	extension is speculative and it is likely that such an extension would fall outside the scope of
	the PhD.

	\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
	the conservation laws}

\end{document}

### 2020-06-19 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

\begin{document}
    \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}

    We begin by considering the evolution of learning with agents who follow a Q-Learning approach.
    Specifically, we look at characterising the stability of agents learning strategies. This
    technique was first carried out by Sanders et al \cite{Sanders}, in which the authors
    characterised the strategy evolution of agents who learn using an 'Experience Weighted
    Attraction' (EWA) algorithm, which is seen to be a strong representation of how people learn in
    games. The authors were able to determine the regions of parameter space in which learning is
    likely to converge towards stable equilibriums, as opposed to complex behaviours (such as limit
    cycles or chaotic dynamics). The aim of this study is to format these techniques for the study
    of computational agents who follow the popular Q-Learning approach \cite{SuttonBarto,Schwarz}.

    We aim, similarly, to determine the regions of parameter space in which the agents are likely to
    converge to stable equilibria. In this way it will be possible to, a priori, determine whether,
    for a particular game, the behaviour is likely to converge and even how to choose the agent or
    game parameters to ensure the predicatability of the resulting behaviour. To achieve this, we
    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{TuylsDynamics}. In this study, the
    authors were able to derive a continuous time dynamical system describing how agents following a
    Q-Learning approach adjust the probabilities of choosing actions as they iteratively play a
    game. These equations are shown in \cite{TuylsDynamics} to accurately model the expected
    behaviour of agents as they iterate a game, and the experiments which verified this model are
    shown in \textbf{Figures ...} .

@@

    \subsection{Research Summary} % \subfile{./sections/ResearchSummary.tex} \label{sec::Research
    % Summary}

@@

    As mentioned, the above system considers only a two player game. This was done with the intention
    of simplifying the notation and reducing the complexity of the experiments. However, the next
    immediate action is to present the equivalent solutions for the case of a general p-player game.
    We then seek to expand this study to a population of agents. For this, we will study the
    stability of the system presented by Leung et al \cite{Leung} which presents a mean-field model
    describing the evolution of learning of a population of Q-Learning agents who play co-operative
    games against one another. This last point is an important limitation - the derived dynamics
    will only consider populations who must co-operate with one another (i.e. the $\Gamma$ value of
    the game is one).

    \section{Control of Swarms with Independent Agents} \label{sec::Independent_Swarm_Control}

    This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
    mode of inquiry upon the completion of the work described in \ref{sec::Chaos_in_Q-Learning}.
    Recall that Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
    through

    \begin{equation}
    \begin{align*}    
        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
        = 0 \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*.
    \end{align*}
    \end{equation}

    In this study we will attempt to formulate an optimal control problem in which the term $F_a[f]
    (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a fixed value
    of $\psi$ to reduce complexity). Note that $F_a$ is dependent on the density function f and so
    we aim to apply feedback controls to the swarm.

>>>>

\begin{document}

    In this chapter, we summarise and present the research and results which have been obtained thus
    far. These tackle the problems described in Section \ref{sec::Chaos_in_MARL}. We detail the
    derivation of a stability phase line as presented in Sanders et al. \cite{Sanders2018} as well
    as the numerical simulations performed to verify these results. The steps to be completed
    subseqent to this study are then given.

    \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}

    We begin by considering the evolution of learning with agents who follow a Q-Learning approach.
    Specifically, we look at characterising the stability of agents learning strategies. This
    technique was first carried out by Sanders et al \cite{Sanders}, in which the authors
    characterised the strategy evolution of agents who learn using an 'Experience Weighted
    Attraction' (EWA) algorithm, which is seen to be a strong representation of how people learn in
    games. The authors were able to determine the regions of parameter space in which learning is
    likely to converge towards stable equilibriums, as opposed to complex behaviours (such as limit
    cycles or chaotic dynamics). The aim of this study is to format these techniques for the study
    of computational agents who follow the popular Q-Learning approach \cite{SuttonBarto,Schwarz}.
    {}
    We aim, similarly, to determine the regions of parameter space in which the agents are likely to
    converge to stable equilibria. In this way it will be possible to, a priori, determine whether,
    for a particular game, the behaviour is likely to converge and even how to choose the agent or
    game parameters to ensure the predicatability of the resulting behaviour. To achieve this, we
    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{TuylsDynamics}. In this study, the
    authors were able to derive a continuous time dynamical system describing how agents following a
    Q-Learning approach adjust the probabilities of choosing actions as they iteratively play a
    game. These equations are shown in \cite{TuylsDynamics} to accurately model the expected
    behaviour of agents as they iterate a game, and the experiments which verified this model are
    shown in \textbf{Figures ...} .

@@

     \textbf{Derivation suppressed, uncomment to see}
     %\subfile{./sections/ResearchSummary.tex}

@@

    As mentioned, the above system considers only a two player game. This was done with the intention
    of simplifying the notation and reducing the complexity of the experiments. However, the next
    immediate action is to present the equivalent solutions for the case of a general p-player game.
    We then seek to expand this study to a population of agents. For this, we will study the
    stability of the system presented by Leung et al \cite{Hu2019} which presents a mean-field model
    describing the evolution of learning of a population of Q-Learning agents who play co-operative
    games against one another. This last point is an important limitation - the derived dynamics
    will only consider populations who must co-operate with one another (i.e. the $\Gamma$ value of
    the game is one).
